Wigglyhedra

### 2024-06-12 draft/wigglyhedra.tex

We refer the reader to \eg~\cite[Sect.~1.3]{bel.ber.del:82} for the definition of a \(t\)-structure on a triangulated category.
The following proposition is easily checked using the calculations in~\cref{rem:generating-morphisms} and standard techniques involving categories of complexes; we omit the proof.
\begin{proposition}
  The pair of subcategories \((\mathcal{C}_m^{\leq 0}, \mathcal{C}_m^{\geq 0})\) forms a bounded \(t\)-structure on \(\mathcal{C}_m\).
\end{proposition}
We call this \(t\)-structure the \defn{standard \(t\)-structure} on \(\mathcal{C}_m\).
Set \(\mathcal{A}_m = \mathcal{C}^{\leq 0}_m \cap \mathcal{C}_m^{\geq 0}\); this is the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, which contains all linear complexes.
It follows that \(\mathcal{A}_m\) is abelian.

@@

\subsection{The Khovanov--Seidel curve model}
\vincent{Add a picture summarizing this section... Asilata drafts it, I will make it.}
In this section we briefly recall how to recover an object of \(\mathcal{C}_{n+1}\) from a wiggly arc on \(n+2\) points on a line.
In fact, the procedure works on more general arcs as well --- namely, those that are not necessarily \(x\)-monotone.
All the results of this section are due to Khovanov and Seidel~\cite{kho.sei:02}.

@@

\subsection{Categorical constraints on compatibility of curves}
In this section, we give a categorical criterion for two wiggly arcs to be compatible as in~\cref{def:compatible}.
As such, this section is somewhat dual to the previous section --- the criterion in this section determines whether a pair of wiggly arcs can belong together in a single wiggly pseudotriangulation, whereas the previous section generated a wiggly pseudotriangulation given any object of the category.
\begin{proposition}
  Consider two wiggly arcs \(\alpha\) and \(\alpha'\), and let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to \(\alpha\) and \(\alpha'\) respectively.
  Then \(\alpha\) and \(\alpha'\) are compatible in the sense of~\cref{def:compatible} if and only if \(\Ext^1(X\langle g \rangle, X\langle g' \rangle) = 0\) for any two integers \(g\) and \(g'\).
\end{proposition}
\begin{proof}
  \asilata{TODO.}
\end{proof}
\begin{remark}
  This proposition is similar to the condition of being compatible in a cluster-tilting object.
  \asilata{Expand and make precise.}
\end{remark}
\begin{remark}
  As stated, this proposition is not expected to be true in greater generality.
  For instance, it does not hold for the zigzag algebra of Dynkin type~$D_4$.
  However, we expect to see similar constraints on compatibility, which we hope to turn to in forthcoming work.
  \asilata{Decide what to say here, because the forthcoming work is far from complete, although I do have counterexamples in type \(D_4\). Discussing how to interpret these counterexamples may not involve too much more work?}
\end{remark}
\begin{question}
  How to best relate this section to the previous one purely categorically?
  That is, given the categorical constraint on compatibility of arcs, is it also clear that it gives a constraint on objects appearing in the cohomology filtration?
  \asilata{Make more precise.}
\end{question}

>>>>

We refer the reader to \eg~\cite[Sect.~1.3]{bel.ber.del:82} for the definition of a \(t\)-structure on a triangulated category.
The following proposition is easily checked using the calculations in~\cref{rem:generating-morphisms} and standard techniques involving categories of complexes; we omit the proof.
\begin{proposition}
  The pair of subcategories \((\mathcal{C}_m^{\leq 0}, \mathcal{C}_m^{\geq 0})\) forms a bounded \(t\)-structure on \(\mathcal{C}_m\).
\end{proposition}
We call this \(t\)-structure the \defn{standard \(t\)-structure} on \(\mathcal{C}_m\).
Set \(\mathcal{A}_m = \mathcal{C}^{\leq 0}_m \cap \mathcal{C}_m^{\geq 0}\) to be the heart of this \(t\)-structure; this is the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, which contains all linear complexes.
It follows that \(\mathcal{A}_m\) is abelian.

@@

\subsection{The Khovanov--Seidel curve model}
\vincent{Add a picture summarizing this section... Asilata drafts it, I will make it.}
In this section we briefly recall how to recover an object of \(\mathcal{C}_{n+1}\) from a wiggly arc on \(n+2\) points on a line.
In fact, the procedure works on more general arcs as well --- namely, those that are not necessarily \(x\)-monotone.

@@

\subsection{Categorical constraints on compatibility of curves}
In this section, we give a categorical criterion for two wiggly arcs to be compatible as in~\cref{def:compatible}.
As such, this section is somewhat dual to the previous section --- the criterion in this section determines whether a pair of wiggly arcs can belong together in a single wiggly pseudotriangulation, whereas the previous section generated a wiggly pseudotriangulation given any object of the category.
\begin{proposition}
  Consider two wiggly arcs \(\alpha\) and \(\alpha'\), and let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to \(\alpha\) and \(\alpha'\) respectively.
  Then \(\alpha\) and \(\alpha'\) are compatible in the sense of~\cref{def:compatible} if and only if \(\Ext^1(X, X') = 0\).
\end{proposition}
\begin{proof}
  \asilata{TODO.}
\end{proof}
\begin{remark}
  This proposition is similar to the condition of being compatible in a cluster-tilting object.
  \asilata{Expand and make precise.}
\end{remark}
\begin{remark}
  As stated, this proposition in combination with~\cref{prop:hn-filtration} is not expected to be true in greater generality.
  For instance, for the zigzag algebra of Dynkin type~\(D_4\), one can find two indecomposable spherical objects with a non-trivial \(\Ext^1\) that nevertheless appear together in the cohomology filtration of another spherical object.
  However, we expect to see similar constraints on compatibility, which we hope to turn to in forthcoming work.
\end{remark}
\begin{question}
  How to best relate this section to the previous one purely categorically?
  That is, given the categorical constraint on compatibility of arcs, is it also clear that it gives a constraint on objects appearing in the cohomology filtration?
  \asilata{Make more precise.}
\end{question}

\asilata{Write something about \(g\)-vectors.}
